---
title: "prelim_analysis"
author: "Gabriel De La Rosa"
date: "7/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(raster)
library(sf)
library(terra)
library(gstat)
library(tmap)
library(here)
```

# Process natural nutrient inputs:
```{r}
# river nutrients
# In kg/yr
  anthro_riverN <- rast(here("plume_outputs", "nitrogen", "anthro_riverN.tif"))
  anthro_riverP <- rast(here("plume_outputs", "phosphorous", "anthro_riverP.tif"))

# outfall nutrients
  # in kg/yr
  # outfall_N <- rast(here("plume_outputs", "outfalls", "outfall_n.tif"))
  out_full_N <- rast(here("plume_outputs", "outfalls", "full_n.tif"))
  out_full_P <- rast(here("plume_outputs", "outfalls", "full_p.tif"))

# Deposition
  # in mgN/m2/yr
  deposition <- rast(here("new_data", "from_nut_hotspots", "nit_dep_1993.tif"))
  # Resample to .008x.008 degrees
  dep_res <- terra::resample(deposition, anthro_riverN, method = "near")
  # Compute cell size in m
  a_008 <- terra::cellSize(anthro_riverN, unit = "m")
  #plot(a_008)
  
  # Convert units:
  dep_kg <- dep_res * a_008 * (1/1000000)
  
 # hist(dep_kg)
  
# plot(dep_kg)
  
# All together in kg/year, summing outfalls  and rivers
  
  anthro_N <- dep_kg + anthro_riverN + out_full_N
  anthro_P <- anthro_riverP + out_full_P
  
  # plot(anthro_N)
  # plot(anthro_P)
```


```{r}
# Load in BO nitrogen:
bo_nit <- raster(here("new_data", "from_nut_hotspots", "bo_nit_2dg.tif"))
bo_phos <- raster(here("new_data", "from_nut_hotspots", "bo_phos_2dg.tif"))

# Interpolate to the coasts:
inter <- function(file){
    r <- file             # Load in the raster
    # grid <- raster::projectExtent(r, res = 0.2)
    xy <- data.frame(xyFromCell(r, 1:ncell(r))) #create a df of the grid
    v = getValues(r) # and a list of the values..
    tmpdf <- cbind(xy, v)%>%filter(!is.na(v)) # Bind them together
    mg <- gstat(id = "v", formula = v~1, locations = ~x+y, data=tmpdf,
              nmax=7, set=list(idp = 2)) # Create a model (power function = 2)
    z <- interpolate(r, mg, progress='text')
}

bo_interN <- inter(bo_nit) %>% 
  rast()
bo_interP <- inter(bo_phos) %>% 
  rast()

# Convert the concentration to kg/cell:
# Original is in micromols/L

##       1 umol/l * 62.0049 g/mol N * 1 mol/1e9 umol = gN/l * 1000 L/1m3 * 1kg/1000g

n_conv <- 62.0049 * 1/1e9 * 1/1000 * 1000/1
p_conv <- 94.9714 * 1/1e9 * 1/1000 * 1000/1

# Convert the whole raster to kg/m3
bo_N_kgm <- bo_interN * n_conv
bo_P_kgm <- bo_interP * p_conv

# Then multiply by the cell size to get just kg per cell:
bo_Nkg <- bo_N_kgm * cellSize(bo_N_kgm)
bo_Pkg <- bo_P_kgm * cellSize(bo_P_kgm)
```

```{r}
# Create a natural nitrogen river plume layer:
# Load in the total river nitrogen:
riverN <- rast(here("plume_outputs", "us_tn_river.tif"))
riverP <- rast(here("plume_outputs", "us_tp_river.tif"))

nat_riverN <- riverN - anthro_riverN
nat_riverP <- riverP - anthro_riverP

# Reclassify so NA's don't give 
# Calculate expansion size
expansion <- .2/.008
# Create template 0.2 degree raster so we can keep coastal values
template <- rast(crs = crs(bo_nit), res = res(bo_nit), extent = ext(bo_nit), vals = 0)

nat_riverN_downscale <- terra::aggregate(nat_riverN, fact = expansion, fun = "mean", na.rm = TRUE)
nat_riverP_downscale <- terra::aggregate(nat_riverP, fact = expansion, fun = "mean", na.rm = TRUE)
# Then aligning the cells
nat_riverN_res <- terra::resample(nat_riverN_downscale, template, method = "near")
nat_riverP_res <- terra::resample(nat_riverP_downscale, template, method = "near")

# Now we can add the kg introduced by rivers to the BO plume layer in kg:
naturalN <- bo_Nkg + nat_riverN_res
naturalP <- bo_Pkg + nat_riverP_res

plot(riverP)

plot(anthro_riverP)

```

# Process anthropogenic inputs:
```{r}
# Aggregate the anthro n layer to 0.2 degree cells, summing values
anthro_n_downscale <- terra::aggregate(anthro_N, fact = expansion, fun = "sum", na.rm = TRUE)
anthro_p_downscale <- terra::aggregate(anthro_P, fact = expansion, fun = "sum", na.rm = TRUE)

# Resample it to the BO layer so the cells align completely
anthro_n_res <- terra::resample(anthro_n_downscale, template, method = "near")
anthro_p_res <- terra::resample(anthro_p_downscale, template, method = "near")
# plot(anthro_n_res)


# This is in kg/kg ### MY natural river nutrient layer is all messed up
ratio <- anthro_n_res/naturalN
ratioP <- anthro_p_res/naturalP

# So do it without:
rato_noriverN <- anthro_n_res/bo_Nkg
ratio_noriverP <- anthro_p_res/bo_Pkg

plot(ratio)
plot(ratioP)

terra::writeRaster(ratio, here("analysis_outputs", "anthro_N_ratio.tif"), overwrite = TRUE)
terra::writeRaster(ratioP, here("analysis_outputs", "anthro_P_ratio.tif"), overwrite = TRUE)
```

# Map it:

### When we look at a bigger map...

## Nitrogen ratio

This is in kg/cell anthropogenic nitrogen / kg/cell natural nitrogen

```{r}
## US shapefile (for plotting)
us_shp <- st_read(here("new_data", "us_shapefile", "US_mainland.shp"))

tmap_mode("view")
tm_shape(ratio_noriverP) +
  tm_raster(style = "jenks", n = 12, title = "Anthropogenic nitrogen to natural nitrogen ratio",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE)
```


## Phosphorus ratio
```{r}
tm_shape(ratio_noriverP) +
  tm_raster(style = "jenks", n = 12, title = "Anthro phosphorus to natural phosphorus ratio",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE) +
  tm_shape(us_shp) +
  tm_polygons(col = "white")
```

# Add in exclusion:
```{r}
# Turn the exclusion layer into a 2 degree grid
exclusion <- rast(here("new_data", "exclusion", "us_exclusion.tif"))

# plot(exclusion)
# by downscaling to the proper res
exclusion_downscale <- terra::aggregate(exclusion, fact = expansion, fun = "mean", na.rm = TRUE)
# Then aligning the cells
exclusion_res <- terra::resample(exclusion_downscale, template, method = "near") 

m <- c(-Inf, 0, 0,
       0.0000001, Inf, 1)

rclmat <- matrix(m, ncol=3, byrow=TRUE)

exclusion_reclass <- exclusion_res %>% 
  terra::classify(rclmat)

plot(exclusion_reclass)
```



```{r}
# Calculate some cell statistics based on the exclusion layer
# By first summing all the nitrogen/phosphorus in the water
totalN <- raster(anthro_n_res)
sumN <- raster::cellStats(totalN, "sum")

totalP <- raster(anthro_p_res)
sumP <- raster::cellStats(totalP, "sum")

# Then calculating how much of that pollutant lies within suitable aquaculture area
availableN <- totalN * raster(exclusion_reclass)
availableP <- totalP * raster(exclusion_reclass)

# First sum the total available N
sum_avN <- raster::cellStats(availableN, "sum")
sum_avP <- raster::cellStats(availableP, "sum")
# Then calculate the percentage available
pct_av_N <- sum_avN/sumN * 100
pct_av_P <- sum_avP/sumN * 100
```

According to a quick calculation, only `r round(pct_av_N, 2)`% of anthropogenic nitrogen inputs fall within available marine space, and only `r round(pct_av_P, 2)`% phosphorus exists in available marine space.

```{r}
# Let's plot this:
tm_shape(availableN) +
  tm_raster(style = "jenks", n = 12, title = "Nitrogen within available space (kg/yr)",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE) +
  tm_shape(us_shp) +
  tm_polygons(col = "white")


tm_shape(availableP) +
    tm_raster(style = "jenks", n = 12, title = "Phosphorus within available space (kg/yr)",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE) +
  tm_shape(us_shp) +
  tm_polygons(col = "white")

```

# What about without including FMP's in the MPA layer?

```{r}
exclusion_nofmp <- rast(here("new_data", "exclusion", "us_exclusion_nofmp.tif"))

# plot(exclusion)
# by downscaling to the proper res
ex_nofmp_downscale <- terra::aggregate(exclusion_nofmp, fact = expansion, fun = "mean", na.rm = TRUE)
# Then aligning the cells
ex_nofmp_res <- terra::resample(ex_nofmp_downscale, template, method = "near") 

m <- c(-Inf, 0, 0,
       0.0000001, Inf, 1)

rclmat <- matrix(m, ncol=3, byrow=TRUE)

ex_nofmp_reclass <- ex_nofmp_res %>% 
  terra::classify(rclmat)
```


```{r}

# Calculate some cell statistics based on the exclusion layer
# By first summing all the nitrogen/phosphorus in the water
totalN <- raster(anthro_n_res)
sumN <- raster::cellStats(totalN, "sum")

totalP <- raster(anthro_p_res)
sumP <- raster::cellStats(totalP, "sum")

# Then calculating how much of that pollutant lies within suitable aquaculture area
av_N_nfmp<- totalN * raster(ex_nofmp_reclass)
av_P_nfmp <- totalP * raster(ex_nofmp_reclass)

# First sum the total available N
sum_avN_nfmp <- raster::cellStats(av_N_nfmp, "sum")
sum_avP_nfmp <- raster::cellStats(av_P_nfmp, "sum")
# Then calculate the percentage available
pct_av_N_nfmp <- sum_avN_nfmp/sumN * 100
pct_av_P_nfmp <- sum_avP_nfmp/sumN * 100
```

According to a quick calculation, only `r round(pct_av_N_nfmp, 2)`% of anthropogenic nitrogen inputs fall within available marine space, and only `r round(pct_av_P_nfmp, 2)`% phosphorus exists in available marine space.

```{r}
# Let's plot this:
tm_shape(av_N_nfmp) +
  tm_raster(style = "jenks", n = 12, title = "Nitrogen within available space (no FMP's) (kg/yr)",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE) +
  tm_shape(us_shp) +
  tm_polygons(col = "white")


tm_shape(av_P_nfmp) +
    tm_raster(style = "jenks", n = 12, title = "Phosphorus within available space (no FMP's) (kg/yr)",
            palette = colorRampPalette( c("lightblue","yellow", "red"))(12),
            legend.hist = TRUE) +
  tm_shape(us_shp) +
  tm_polygons(col = "white")

```
