---
title: "nutrient_pollution"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(raster)
library(tidyverse)
library(here)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(rgdal)
library(lwgeom)
library(sf)
library(maptools)

rasterOptions(maxmemory = 1e10, progress = "text")
```

### This just straight up needs to be redone...



## What about the Sparrow model?


## This transforms the pacific stream reaches that were used in SPARROW into a useful df & proj
```{r}
# We need to associate the comid identifiers with actual stream locations.
reaches_pac <- read_sf(here("data", "SPARROWmodelinp", "PAC_REACHES"), layer = "PAC_REACHES")
# We need to drop the M dimension of this file...
reaches_pacXYZ <- st_zm(reaches_pac, what = "ZM")
# But this is in albers equal area...
# Let's reproject to wgs84
proj <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
reaches_proj <- st_transform(reaches_pacXYZ, proj)
```

### This takes NOAA's published stream reaches, selects only terminal reaches that contact the coastline, and then turns them into points (outflows) on the coastline.
### Why do I need to use the second reach dataset? Because the first has no indicator of whether a reach is a terminal flowline or not!

##### Stream reaches Downloaded from here:
This is seamless flattened lower 48 flowlines:
https://s3.amazonaws.com/edap-nhdplus/NHDPlusV21/Data/NationalData/NHDPlusV21_NationalData_Seamless_Geodatabase_Lower48_07.7z

```{r}
# Can we just extract terminal streams from the gdb?
# Let's see whats in this gdb
ogrListLayers(here("data", "NHDPlusNationalData", "NHDPlusV21_National_Seamless_Flattened_Lower48.gdb"))
# We want NHDFlowline_Network
# Read in the NHD flowline network
flowline <- readOGR(here("data", "NHDPlusNationalData", "NHDPlusV21_National_Seamless_Flattened_Lower48.gdb"), "NHDFlowline_Network")
#And select only flowlines that have been classified terminal flowlines
flow_terminal <- flowline %>% 
  as.data.frame() %>%  
  filter(TerminalFl == 1)
# And we can pull just the COMIDs from these.
flow_comids <- flow_terminal %>%
  dplyr::select("COMID") %>% 
  mutate(terminal = TRUE)
# If we join this to the reaches_proj dataset...
reaches_terminal <- inner_join(reaches_proj, flow_comids, by = "COMID") %>% 
  st_as_sf()
# We get all the terminal reaches used in the SPARROW mode. Some are still land-based.
#cplot(reaches_terminal)
```

# This code reads in the ocean reaches:
```{r}
reaches_terminal <- read_sf(here("scratch"), layer = "pac_term_reaches")

# In GIS (for speed), I buffered the coastline by 100 m and then selected all the stream reaches that intersected that buffer.
## Shoreline_selectt is a 100m buffer using the NOAA medium resolution shoreline
## Ocean reaches is a 1km buffer from the EEZ, which is too coarse
ocean_reaches_pac <- as.data.frame(read_sf(here("scratch", "ocean_reaches"), layer = "shoreline_selectt"))

# And we can join them to the terminal reaches, keeping only terminal reaches within 100m of the ocean.
final_reaches <- inner_join(reaches_terminal, ocean_reaches_pac, by = "COMID") %>% 
  select("COMID", "geometry.x") %>% 
  st_as_sf()
# This ignores puget sound but looks good everywhere else

# We can next sample the endpoints for each line:
# First, turn all the complex lines into straght ones
reaches_simple <- st_simplify(final_reaches)
# Find the nearest points to our EEZ: using the st_startpoint function in the lwgeom package

reach_starts <- reaches_simple %>% 
  mutate(geometry = st_startpoint(reaches_simple)) %>% 
  as.data.frame() %>% 
  dplyr::select("COMID", "geometry") %>% 
  st_as_sf

```


```{r}

#### DO I NEED THIS??
### IDK

# We can recycle the function that snaps points to a polygon here...
st_snap_points <- function(x, y, namevar, max_dist = 1000){
  # this evaluates the length of the data
  if (inherits(x, "sf")) n = nrow(x)
  if (inherits(x, "sfc")) n = length(x)
  # this part: 
  # 1. loops through every piece of data (every point)
  # 2. snaps a point to the nearest line geometries
  # 3. calculates the distance from point to line geometries
  # 4. retains only the shortest distances and generates a point at that intersection
  out = do.call(c,
                lapply(seq(n), function(i) {
                  nrst = st_nearest_points(st_geometry(x)[i], y)
                  nrst_len = st_length(nrst)
                  nrst_mn = which.min(nrst_len)
                  if (as.vector(nrst_len[nrst_mn]) > max_dist) return(st_geometry(x)[i])
                  return(st_cast(nrst[nrst_mn], "POINT")[2])
                })
  )
  # this part converts the data to a dataframe and adds a named column of your choice
  out_xy <- st_coordinates(out) %>% as.data.frame()
  out_xy <- out_xy %>% 
    mutate({{namevar}} := x[[namevar]]) %>% 
    st_as_sf(coords=c("X","Y"), crs=st_crs(x), remove=FALSE)
  
  return(out_xy)
}

# Apply the function to snap points to the EEZ:
reach_snap <- st_snap_points(reach_starts, eez, namevar = "COMID")
plot(reach_snap)
```

### Joining the coastline reaches to nutrient data:
```{r}
# Read in nutrient data from the SPARROW model:
sparrow_pac <- read_csv(here("data", "SPARROWmodelinp", "pac_sparrow_model_output_tn.txt"))
# Select the nitrogen (kg/yr) and the stream reach identifiers (comid)
sparrow_tn_pac <- sparrow_pac %>% 
  select("comid", "al_tn")
# Join these values to the reach outlets
pac_join <- inner_join(sparrow_tn_pac, reach_starts, by = c("comid" = "COMID"))
# Turn into an sf object
pac_joinsf <- st_as_sf(pac_join)

# We can read in our ocean raster:
ocean <- raster("ocean_mask_landnull.tif")
# Turn this into a polygon:
ocean_poly <- rasterToPolygons(ocean)
o_poly_sf <- st_as_sf(ocean_poly)
plot(ocean_poly)
# And try and snap the points to the nearest point on the polygon:
# Using this function..
st_snap_points = function(x, y, max_dist = 1000) {
  if (inherits(x, "sf")) n = nrow(x)
  if (inherits(x, "sfc")) n = length(x)

  out = do.call(c,
                lapply(seq(n), function(i) {
                  nrst = st_nearest_points(st_geometry(x)[i], y)
                  nrst_len = st_length(nrst)
                  nrst_mn = which.min(nrst_len)
                  if (as.vector(nrst_len[nrst_mn]) > max_dist) return(st_geometry(x)[i])
                  return(st_cast(nrst[nrst_mn], "POINT")[2])
                })
  )
  return(out)
}

## THIS TAKES FOREVER
## pac_n_snap <- st_snap_points(pac_joinsf, o_poly_sf)

# i can join the COMID from pac_joinsf to the snapped point geometries:
pac_n_snap[1]
snap_df <- data.frame(pac_n_snap) %>% 
  cbind(pac_joinsf$comid) %>% 
  st_as_sf() %>% 
  rename(comid = "pac_joinsf$comid")

# ...Woohoo. I still need to join this back to each
  
st_write(pac_n_snap, here("scratch", "pac_river_snap.shp"))

```




####### PLUME MODELING:::

From Warwick et al., 2004:
 https://doi.org/10.1029/2003GL019114
 
 
 Plumea area is related to the area of the watershed that flows into the river as:
 
 $P = cA^\b$
 
 where c is a plume size factor related to discharge (0.5-2 for moderate flows) 
 
 and b is 0.65
 
 c is estimated to be 0.5 by Warrick et al. 2017. for rivers without coastal influence.
 https://www.sciencedirect.com/science/article/pii/S0079661116300532?via%3Dihub#!
 
 
What to do with this?

Calculate plume area for each plume.
Select adjacent cells until the total plume area is covered
Then...diffuse total kg across those cells?
  Scaling 

in sparrow_pac:

* CumAreaKM2 is the cumulative upstream watershed area for each reach.

* al_tn_scg = scrub and grassland
* _atm is atmospheric disposition ()
* _urb is urban land
* _ald is red alder trees
* _fert is fertilizer
* _wwtp is wastewater
* DEL_FRAC is the fraction delivered downstream...

```{r}

### THIS IS ALL FUCKED
# Read in the snapped data...
pac_n_snap <- read_sf(here("scratch"), layer = "pac_river_snap")
# These are terminal reaches
pac_reaches <- read_sf(here("scratch"), layer= "pac_term_reaches")
sparrow_pac <- read_csv(here("data", "SPARROWmodelinp", "pac_sparrow_model_output_tn.txt"))

sparrow_final <- sparrow_pac %>% 
  select("comid", "al_tn", "CumAreaKM2")

which.max(sparrow_pac$CumAreaKM2)

test <- sparrow_pac[249714,]
# Rejoin to the COMID's:

snap_df <- pac_n_snap %>% 
  mutate(comid = reach_starts$COMID)

# Then add the total nitrogen to this, also CumAreaKM2
snap_n_a <- sparrow_pac %>% 
  select("comid", "al_tn", "CumAreaKM2") %>% 
  inner_join(snap_df, by = "comid")


test_plume_df <- head(snap_n_a, 10) %>% 
  st_as_sf()

eez <- raster(here("new_data", "ocean_masks", "ocean_mask_landnull.tif"))
# Run this for the plume model.....


# Turn it into sp...
test_plume_spat <- as_Spatial(test_plume_df)

ocean_polygon <- rasterToPolygons(eez)

crs(ocean_polygon) <-  432
plot(ocean_polygon)

test_plume_snap <- maptools::snapPointsToLines(points = test_plume_spat, lines = ocean_polygon)




plume_fx(points = test_plume_df,
         raster = eez,
         path = here("scratch", "test_plume"))

test_rast <- raster(here("scratch", "test_plume", "1671441.tif"))

plot(test_rast)
```

```{r}
plume_fx <- function(points, raster, c = 0.5, b = 0.65, path){

# points = snap_n_a[10,]
# raster = eez
# path = here("scratch", "test_plume")  
  
    # So there's only one row:
    for(i in 1:nrow(points)){
    
      test_pt <- points[i,]
      name <- paste("plume_", i, ".tif", sep = "")
      path2 <- paste(path, points$comid, sep = "/")
      
      ### THIS HAPPENS ONCE
      # Get which cell contains that point
      cell <- cellFromXY(raster, st_coordinates(test_pt$geometry))
      # Duplicate the OG raster
      newraster <- raster
      # Set point = 1
      newraster[cell] <- 1
      
      # Calculate plume area: in KM2
        c <- 0.5
        b <- 0.65
        p_area <- c*(test_pt$CumAreaKM2^b) *1000
      
      ### THIS REPEATS
       tot_area <- 0
       n_runs <- 1
      repeat {
        # get cell names for cells that are 1
        newcell <- Which(newraster>=1, cells = TRUE)
        # Find adjacent cells
        adj <- adjacent(newraster, newcell, directions = 4, pairs = FALSE)
        # Turn them into ones
        newraster[adj] <- 1
        # Create a new "newraster" with new ones:
        newraster <- newraster+raster
        tot_area <- sum(as.vector(area(newraster)*newraster), na.rm = TRUE)
        n_runs <- n_runs+1
        # Repeat function until the area is bigger than the plume:
        if(tot_area >= p_area) break}
     
    ###
    ### PLUMING
    ###
       
     # Then I actually need to plume these into the ocean.
       
     # Get the effluent as a value
     effluent <- test_pt$al_tn
     # Get the proportion of effluent included in each expansion
     prop_eff <- effluent/n_runs
     
     # Create a plume raster:
     p_raster <- raster
     final <- raster
     final[cell] <- prop_eff
      # Set OG point = effluent
     p_raster[cell] <- 1
     # Then, loop through again:
     p_runs <- 1
     repeat{
        # get cell names for cells that are 1
        p_cell <- Which(final>=1, cells = TRUE)
        # Find adjacent cells
        adj <- adjacent(p_raster, p_cell, directions = 4, pairs = FALSE)
        # Turn them into ones
        p_raster[adj] <- 1
        # Set OG cells to NA's
        p_raster[p_cell] <- NA
        # Get cell numbers for new cells
        e_cell <- Which(p_raster>=1, cells = TRUE)
        # Add effluent proportionally over the new cells
        final[e_cell] <- prop_eff/length(e_cell)
        final <- final + raster
        
        # Conditional for loop ending
        p_runs <- p_runs+1
        # Repeat function until the area is bigger than the plume:
        if(p_runs >= n_runs) break}
     
     writeRaster(final, path2, format = "GTiff", overwrite = TRUE)
    }
  }
```
